---
title: "p8106_hw4"
author: "David DeStephano"
date: "April 25, 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(caret) # only for plot
library(lasso2) # only for data
library(tidyverse)

library(ISLR)
library(rpart) #cart
library(rpart.plot)
library(party)
library(partykit)
library(randomForest)
library(ranger)
library(gbm)
library(plotmo)
library(pdp)
library(lime)
```


```{r}
data(Prostate)

```

#Part A: Fitting a regression tree to prostate data
```{r}
set.seed(1)
tree1 <-rpart(formula = lpsa~., data = Prostate)
rpart.plot(tree1)

cpTable <-printcp(tree1)
plotcp(tree1)
minErr <-which.min(cpTable[,4])
#minimum cross-validation error
min_tree <-prune(tree1, cp = cpTable[minErr,1])
rpart.plot(min_tree)


# 1SE rule
se_tree <-prune(tree1, cp =
                cpTable[cpTable[,4]<cpTable[minErr,4]+cpTable[minErr,5],1][1])


rpart.plot(se_tree)


```


The tree size that corresponds to the lowest cross-validation error is 8, using the 1 SE error rule the tree size is 3. 

#Part B: plot the final tree

When looking at the plotcp, the left most value where the mean is below the horizontal line is 3. This corresponds to the pruned tree using the 1 SE rule,so this is the tree that will be used. This model suggests that lcavol is the only predictor of importance when predicting lpsa and keeping at a reasonable error rate.

```{r}
rpart.plot(se_tree)
```

Interpretation of terminal node 1: When lcval is less than -.48, the mean lpsa is 2.3. This node contains 9% of the sample.

#Part C Bagging

```{r}
#Create training and test data
set.seed(1)
train = sample(1:nrow(Prostate), nrow(Prostate)/2)
#Use all variables for mtry
bagging <-randomForest(lpsa~., Prostate, subset=train,
                       mtry = 8, importance=TRUE)

bagging$importance
```


#Part D Random Forest
```{r}
set.seed(1)
#Use number of variables divided by three rounded down
rf <-randomForest(lpsa~., Prostate, subset=train,
                  mtry = 2, importance=TRUE)
rf$importance
```


#Part E Boosting
```{r}
set.seed(1)

bst <-gbm(lpsa~., data=Prostate[train,],
          distribution = "gaussian",
          n.trees = 5000,
          interaction.depth = 3,
          shrinkage = 0.005,
          cv.folds = 10)

ensemble.nt <-gbm.perf(bst, method = "cv")


```

#PArt F compare models

```{r}
prostate.test=Prostate[-train,"lpsa"]

#Bag
yhat.bag = predict(bagging,newdata=Prostate[-train,])
plot(yhat.bag, prostate.test)
abline(0,1)
mean((yhat.bag-prostate.test)^2)

#RF
yhat.rf = predict(rf,newdata=Prostate[-train,])
plot(yhat.rf, prostate.test)
abline(0,1)
mean((yhat.rf-prostate.test)^2)


#Boost
yhat.boost=predict(bst,newdata=Prostate[-train,],n.trees=5000)
plot(yhat.boost, prostate.test)
abline(0,1)

mean((yhat.boost-prostate.test)^2)



```


From the models fitted above, I would choose the bagged model as it has the lowest MSE, however, the boosted model should theoretically perform best, so if this were a project for work I would likely tune the model more carefully and chose a different corssvalidation method, and I would then expect the boosted model to perform best.

